\documentclass[10pt]{article}

\usepackage[top=2cm, bottom=2cm, left=2cm, right=2cm]{geometry}
\usepackage{enumitem}

\setlength{\parindent}{0cm}
\setlist[itemize]{leftmargin=1.5em}

\begin{document}

\title{John Doe}
\author{Curriculum Vitae}
\date{2014-05-16}

\maketitle

\section*{Personal data}

Dr John Doe 

42., Home Street st., Home Town, 00000, United Earth

johnny@example.com

555-HOME, 555-CVCV

http://example.com/john.doe

\section*{Education}

\begin{itemize}
  \item MSc in Temporal Mechanics, Department of Temporal Mechanics, Starfleet Academy, United Earth, 2014. MSc thesis: "Deconstructing Lamport Clocks ".
  \item BSc in Transporter Theory, Department of Transporter Theory, Starfleet Academy, United Earth, 2013. BSc thesis: "A Simulation of Vacuum Tubes".
\end{itemize}

\section*{Languages}

\begin{itemize}
  \item English, Certificate of Proficiency.
  \item Klingon, Imperial Certificate of Mastery.
\end{itemize}

\section*{Research experience}

\begin{itemize}
  \item 01/2014--present: Postdoctoral research in "The Impact of Unstable Methodologies on Cyberinformatics", Department of Robotics, Starfleet Academy, United Earth.
  \item 01/2013--12/2013: Research work for the "Lossless, Adaptive Symmetries for Internet QoS" research project, Department of Stellar Cartography, Starfleet Academy.
\end{itemize}

\section*{Selected publications}

\begin{itemize}
  \item Doe, J., "Enabling the Ethernet and XML", Interstellar Journal of  Exobiology/Xenobiology, Vol. 42, N19, pp. 128-256, Starfleet Publishing, 2013.
  \item Surname, N. and Colleague, X., "On the Synthesis of Thin Clients", 11th Interstellar Conference on Advanced Subspace Geometry, United Earth, 2004.
\end{itemize}

\section*{Organizations}

\begin{itemize}
  \item Department of Temporal Investigations, United Federation of Planets, regular member.
\end{itemize}

\section*{Professional experience}

\begin{itemize}
  \item 1/1/2013--31/12/2013: Starfleet Academy, Lecturer, "Plasma Physics" course.
  \item 1/1/2014--present: USS Enterprise (NCC-1701-D), Captain.
\end{itemize}

\section*{Hobbies and interests}

\begin{itemize}
  \item Xenolinguistics, virtual world design for the Holodeck.
\end{itemize}

\end{document}
